---
format: gfm
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = TRUE,
  echo = TRUE,
  comment = "#>",
  fig.path = "vignettes/vignette-",
  message=FALSE,
  warning=FALSE
)
# pkgdown::build_site()
```

# Rinteract

[![R-CMD-check](https://github.com/jonfoong/Rinteract/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jonfoong/Rinteract/actions/workflows/R-CMD-check.yaml)[![codecov](https://codecov.io/github/jonfoong/Rinteract/branch/main/graph/badge.svg?token=2SOK4T1220)](https://codecov.io/github/jonfoong/Rinteract)[![CRAN status](https://www.r-pkg.org/badges/version/Rinteract)](https://CRAN.R-project.org/package=Rinteract)[![License: GPL-3](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://cran.r-project.org/web/licenses/GPL-3)[![](https://img.shields.io/badge/devel%20version-0.1.0-blue.svg)](https://github.com/jonfoong/Rinteract)

Rinteract is a small package that makes it easy to output all conditional effects in models with interaction terms instead of computing hypothesis tests manually.

## Installation

```{r install, eval=FALSE}

devtools::install_github("jonfoong/Rinteract")
```

## Overview

Interaction terms are widely used in regression models to uncover underlying heterogeneity for a predictor of interest. Despite its ubiquity, interpretation of interaction models is often confusing at best and inaccurate at worst. In addition, studies with interaction terms typically only report estimates from a model output. As pointed out by Brambor et al (2006):

> ...typical results table often conveys very little information of interest because the analyst is not concerned with model parameters per se; he or she is primarily interested in the marginal effect of X on Y for substantively meaningful values of the conditioning variable Z. While it is often possible to calculate the marginal effect of X for any value of Z from the typical results table using a little algebra, the problem is that it is not possible to do the same for the standard errors.

`Rinteract` avoids this by computing all conditional effects in a model with interactions. It accepts a model object as input and relies on `multcomp` to perform hypothesis testing on all conditions of interest (when a variable is at 0, 1, or the mean). It is also capable of graphing these effects using tabular ggplots.

Note: As of now the package only accepts `lm`, `glm` and `lm_robust` models.

## Usage

```{r}
library(Rinteract)
library(kableExtra)

mod <- lm(Y~X1*X2*X3, toydata)
dat <- int_conditions(mod, toydata)
dat |> 
  head() |>
  kable(digits = 3)


```

We can then graph the result:

```{r}
#| fig.width: 10
#| fig.height: 6

library(ggplot2)

int_graph(dat, X1~X2+X3) +
  ggtitle("test")

```
